Functory: Distributed Computing \\ for the Common Man\thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2010-10-12 doc/jfla-2001/main.tex
*** empty log message ***

\documentclass[a4paper,12pt]{article}

% The following \documentclass options may be useful:
%
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% authoryear    To obtain author/year citation style instead of numeric.

\usepackage{fullpage,comment,amsmath,graphicx,color,url}

@@

\begin{document}

\title{Functory: Distributed Computing \\ for the Common Man\thanks{This
    research was partly supported by the French national project U3CAT
    (\emph{Unification of Critical C Code Analysis Techniques},
    ANR-08-SEGI-021).}} 
%\subtitle{Subtitle Text, if any}

\author{Jean-Christophe Filli\^{a}tre \quad K. Kalyanasundaram \\
  CNRS, LRI, Univ Paris-Sud 11, Orsay F-91405\\
  INRIA Saclay - \^{I}le-de-France, ProVal, Orsay, F-91893 \\
   \url{filliatr@lri.fr, kalyan.krishnamani@inria.fr}}

\maketitle

>>>>

\documentclass[twoside]{article}

\usepackage{actes,comment,amsmath,graphicx,color,url}
\usepackage[french]{babel}
\usepackage[latin1]{inputenc}
%\usepackage[T1]{fontenc}

@@

\title{Functory: Distributed Computing \\ for the Common Man\thanks{This
    research was partly supported by the French national project U3CAT
    (\emph{Unification of Critical C Code Analysis Techniques},
    ANR-08-SEGI-021).}}

\author{Jean-Christophe Filli\^{a}tre$^{1,2,3}$ \& K. Kalyanasundaram$^3$}

\titlehead{Functory}%  a droite (page impaire)

\authorhead{Filliâtre \& Kalyanasundaram}% a gauche (page paire)

\affiliation{\begin{tabular}{rr} 
\\ 1:  CNRS / LRI UMR 8623 F-91405 Orsay
\\ 2:  Université Paris Sud F-91405 Orsay
\\ 3:  INRIA Saclay -- Île-de-France F-91893 Orsay
\\ {\tt filliatr@lri.fr},  
   {\tt kalyan.krishnamani@inria.fr}
\end{tabular}}

\begin{document}
\setcounter{page}{1}
\maketitle
